The impact of cosmic variance on constraining the mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z \sim 3$

### 2014-03-28 paper/ms.tex
shorter
new abstract

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density distribution and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
1.0$. We use this approach to avoid the uncertainties associated
  to the estimation of \ly luminosities in each halo. Our analysis
shows that the clustering and number density information are
insufficient to impose a tight constraint on the occupation
fraction. On the other hand, the minimum mass and maximum mass can be
constrained to the range $M_{\rm  max}<10^{12}$\hMsun\ and
$10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$. We also find
that the consistent models have a narrow mass range, $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, smaller than $1.0$ dex,
with a majority in the range $\Delta M<0.5$ dex. These results
  broadly reproduce some constraints   already presented in the
  literature. However, the wide range of values for the occupation
  fraction and the narrow mass range $\Delta M$ are novel results from
  the approach presented here. We conclude that achieving a constraint on the
occupation fraction for LAEs at $z=3.1$ will require observations on
larger fields to reduced cosmic variance and robust physical models
for the connection between dark matter, star formation and the escape
of \ly radiation. That kind of modeling should also be able to provide
a plausible explanation for the narrow mass range derived here for the
halos hosting LAEs at $z=3.1$. 
\end{abstract}

>>>>

\begin{abstract}
%
  We study the impact of cosmic variance in constrainng the mass and
  occupation fraction of dark matter halos hosting \ly Emitting
  Galaxies at high redshift. We use and N-body simulation to construct
  mock fields with the same typical size of observed fields at
  $z=3.1$. As a benchmark we match the observed number density
  distribution across fields and the angular correlation function. To
  populate the halos in the simulation we use a model where a dark
  matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm
    max}$ can only host one detectable LAE with a probability $0.1
  \leq f_{\rm occ}\leq 1.0$.  Our analysis shows that the clustering
  and number density information are insufficient to impose a tight
  constraint on the occupation fraction. On the other hand, the
  minimum mass and maximum mass can be constrained to the range
  $M_{\rm  max}<10^{12}$\hMsun\ and $10^{10.2}\hMsun\leq M_{\rm
    min}\leq 10^{11.5}\hMsun$. We also find that the consistent models
  have a narrow mass range, $\Delta M \equiv \log_{10}M_{\rm max} -
  \log_{10} M_{\rm min}$, smaller than $1.0$ dex, with a majority in the range $\Delta M<0.5$ dex. These results
  fall into constraints   already presented in the
  literature. However, the wide range of values for the occupation
  fraction and the narrow mass range $\Delta M$ are novel results from
  the approach presented here. We conclude that achieving a constraint on the
  occupation fraction for LAEs at $z=3.1$ will require observations on
  larger fields to reduced cosmic variance and robust physical models
  for the connection between dark matter, star formation and the escape
  of \ly radiation. 
\end{abstract}
